A preliminary constraint grammar for Russian

### 2015-05-04 2015-nodalida-ruscg/ruscg.tex
adding references
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60216 72bbbca6-d526-0410-a7d9-f06f51895060

Given that just over half of all ambiguity remains after running our preliminary constraint
grammar and that for many applications unambiguous output is necessary, we decided to 
experiment with combining the constraint grammar with a statistical tagger to resolve remaining
ambiguity.

@@

\rr{R1: Note that Johannessen et al (2012) and Lynum et al (2011) have written two articles about building a statistical tagger on top of a cg grammar.

Johannessen, Janne Bond; Hagen, Kristin; Lynum, André; Nøklestad, Anders. 2012. OBT+stat: A combined rule-based and statistical tagger. In Andersen, Gisle (ed.). Exploring Newspaper Language: Using the web to create and investigate a large corpus of modern Norwegian, s. 51–66.

Lynum, Andre; Hagen, Kristin; Johannessen, Janne Bondi; Nøklestad, Anders. OBT+Stat: Evaluation of a combined CG and statistical tagger. In NEALT Proceedings Series 2011 Vol. 14.}

>>>>

Given that just over half of all ambiguity remains after running our preliminary constraint
grammar and that for many applications unambiguous output is necessary, we decided to 
experiment with combining the constraint grammar with a statistical tagger to resolve remaining
ambiguity. Similar approaches have been taken by previous researchers with Basque \cite{ezeiza.ea-98}, Czech \cite{hajic.ea-01,hajic.ea-07}, Norwegian \cite{johannessen.ea-11,johannessen.ea-12}, Spanish \cite{hulden12}, and Turkish \cite{oflazer.tur-96}.

@@
